---
title: "Corvina Reina Gulf of Nicoya Zone 201 2012"
output:
  html_document:
    toc: true
    toc_depth: 2
---
##Setup

```{r setup, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(reshape)
library(ggplot2)
library(lubridate)
library(plotly)

```


```{r length_dist_2012}

corvina.all.2012.short<- read.csv('./data/corvina_length_monthly_2012.csv') 
corvina.all.2012.short$date = as.Date(corvina.all.2012.short$date, "%m/%d/%y")

corvina.all.2012 <- untable(corvina.all.2012.short[ , c(1,4)], num=corvina.all.2012.short[ ,5]) %>%
  mutate(label = month.abb[month(date)])

```

## Length Composition Corvina Reina 2012

```{r plot}

p1<- ggplot(corvina.all.2012, aes(length_class, fill=factor(label, levels =    unique(label)))) +
    geom_histogram(binwidth = 1) +
    theme_minimal()+
    guides(fill=guide_legend(title="Month"))
   
ggplotly(p1)

```
  
<spacer> 

## Age at length

This is two different approaches to convert lengths to age. The first is a formula I got from someone elses code. The second is the equation from [FAO](http://www.fao.org/docrep/w5449e/w5449e06.htm#4.4.5 the linearized catch curve based on length composition data):

$$t(L)=t_0 - 1/K * ln(1-L/L_{inf})$$


 ** the second seems better because we know that length/ age at maturity if 55 cm/5 years
```{r age_at_length}
#Model parameters fom Mug Villanueva (1994)
#Used the lower bound of the range

Linf = 122.1
to = -0.136
K = 0.121

#Equation from Dan's code
corvina.age1 <- log(1-(pmin(corvina.all.2012$length_class, Linf*.99))/(-K)) + to

#Equation from FAO 
#(http://www.fao.org/docrep/w5449e/w5449e06.htm#4.4.5 the linearized catch curve based on length composition data)

corvina.age2 <- to - (1/K) * log(1-corvina.all.2012$length_class/Linf)

corvina.all.2012$age_class1 = corvina.age1

corvina.all.2012$age_class2 = corvina.age2

```

```{r plot_length_age}
corvina.age.length <- unique(corvina.all.2012[,c('length_class','age_class2')]) %>%
  dplyr::arrange(length_class)


ggplot(data = corvina.age.length, aes(x=age_class2, y=length_class)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Age years (age_class2)", y = "Length class (1 cm bins)")

```


## Age Composition Corvina Reina 2012

```{r plot_age}

p2<- ggplot(corvina.all.2012, aes(age_class2, fill=factor(label, levels =    unique(label)))) +
    geom_histogram(binwidth = 1) +
    theme_minimal()+
    guides(fill=guide_legend(title="Month"))
   
ggplotly(p2)

```
  

## Time to next size class (D)
  
"In the present context D t is the time it takes for an average fish to grow from length L1 to length L2, so we obtain D t by subtracting the two inverse von Bertalanffy equations (Eq. 3.3.3.2) corresponding to L2 and L1 respectively and obtain:"

$$\Delta t = t(L_2) - t(L_1) = \frac{1}{K} * ln\Big(\frac{L_{inf}-L_1}{L_{inf}-L_2}\Big)$$

```{r calculating_D}
#Vector to label L1 - L2 
L1.L2 <-vector(length=length(corvina.age.length$length_class))

#Vector to identify if difference in length classes is greater than 1
delta <- vector(length=length(corvina.age.length$length_class))

#Vector of the time it takes to grow from L1 to L2
D <- vector(length=length(corvina.age.length$length_class))

#Vector for the x axis of linearized catch curve (I dont understand it conceptually yet)
x <- vector(length=length(corvina.age.length$length_class))

for (i in 1:length(corvina.age.length$length_class)){
  
L1 <- corvina.age.length[i,1]

L2 <- corvina.age.length[(i+1),1]
  
L1.L2[i] <-paste(L1, L2, sep="-") 

delta[i] <- L2 - L1

D[i] <- (1/K)*log((Linf-L1)/(Linf-L2))
 
  #this equation for D is the same as saying:
  #corvina.age.length[(i+1),2] - corvina.age.length[i,2]

x[i] <- to - (1/K)*(log(1-((L1+L2)/(2*Linf))))



}

table <- data.frame(L1.L2, D, delta)

```



```{r plot_D, warning= FALSE}

corvina.age.length$D <- D/delta
corvina.age.length$x <- x


ggplot(data = corvina.age.length, aes(x = length_class, y = D)) +
  geom_point() +
  theme_minimal() +
  labs(y="Time to next length class (D) ")

```


```{r show_D, fig.width=4}

library(DT)
datatable(table, options = list(
                            pageLength = 5, 
                            autoWidth = TRUE))

```


##Catch Curve 

following steps from FAO:
  
Table 4.4.5.1 Linearized catch curve based on length composition data
  
```{r Linearized_catch_curve_data}
#Gathers all the lengths into a df of length classes and total counts for 2012 (all gear types)

corvina.catch.curve<- corvina.all.2012.short[,4:5] %>%
                        dplyr::group_by(length_class) %>%
                        dplyr::summarise(count_total = sum(count))

#adds age value (years) with matching length and annual count value
corvina.catch.curve$age <- corvina.age.length$age_class2

#adds "delta t" - time to next length class

corvina.catch.curve$D <- D
      
corvina.catch.curve$x <- x

corvina.catch.curve$y <- log(corvina.catch.curve$count_total/corvina.catch.curve$D)

#Sets Length at first capture to the mode of the length dist

Lc <- corvina.catch.curve$length_class[which.max(corvina.catch.curve$count_total)]

# filters out all lengths smaller than Lc

corvina.catch.curve <- dplyr::filter(corvina.catch.curve, length_class >= Lc)

```

$$x = t\Big(\frac{L_1 + L_2}{2}\Big) = t_0 - \frac{1}{K} * ln\Big(1-\frac{L_{1}+L_2}{2L_{inf}}\Big)$$

$$y = ln\Big(\frac{C(L_1, L_2)}{\Delta t(L_1, L_2)}\Big)$$

```{r test_plot_catch_curve}

catch.curve.model <- lm(y~x, corvina.catch.curve)

Z <- catch.curve.model$coefficients[2]

SE <- 0.01756

ggplot(corvina.catch.curve, aes(x= x, y=y)) +
  geom_point()+
  stat_smooth(method = lm) +
  theme_minimal() +
  annotate("text", x= 12, y= 6, label = paste("- Z = ", paste((round(Z, digits = 4)) , SE, sep = " ± ")))
  
  

```

