---
title: "R Notebook"
output: html_notebook
---
##Deterministic Age-Stuctured Model

###Parameters
 *Linf* - Von Bertalanffy asymptotic length
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical theoretical age when length is zero  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- natural mortality  
 *F* - fishing mortality  

###Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())


#Set Model----
NumYears = 25

R0 = 100

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.3
  
Wb = 2.824
  
#Length (cm) at which a fish is 50/95 percent vulnerable to fishing mortality
S50 = 26

S95 = 29

#Length (cm) at which a fish is 50/95 percent likely to be mature
m50 = 55

m95 = 62.7

#Natural mortality
M <- 0.258

#Fishing mortality
F <- 0.3125

#Spawners per Recruit

h <- 0.7


BHa <- 0.546 #this is made up
  
BHb <- 0.000089 #this is made up
  
```

Size-depemdent two-parameter logistic function for vulnerability and maturity

###Vulnerabiltity to fishery
$$Va = \frac{1}{1-e^{-ln(19)\frac{L_1 - S_{50}}{S_{95} - S_{50}}}}$$

###Probability of being mature
$$Ma = \frac{1}{1-e^{-ln(19)\frac{L_1 - m_{50}}{m_{95} - m_{50}}}}$$


```{r Data}

#Our max age is 18 years
Age <- seq(1,18,1)

Length <- Linf*(1-exp(-K*(Age-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb


Va = 1/(1 + exp(-log(19)*((Length - S50)/(S95 - S50))))

Ma =  1/(1 + exp(-log(19)*((Length - m50)/(m95 - m50))))

#realtive fecundity - corvina produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- 41*Weight


#Price per kg is dependent on size of fish
Price <- c(10,50,100)
```


```{r Data Structures}
N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))
colnames(N_at) = as.character(c(Age))

Recruitment <- vector(length = NumYears)

Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears))
colnames(Catch) <- as.character(c(Age,'Total'))
                        

Revenue <- data.frame(matrix(data = NA, ncol = 4, nrow = NumYears))
colnames(Revenue) =c('small',
                     'med',
                     'large',
                     'total')

```

### Instantaneous mortality (*Z*)
$$Z_a = M + V_aF $$

###Abundance N of age *a* in time *t*

\usepackage{amsmath}
...
...
$$
N_{a,t} =
\begin{cases}
R_t, & \text{if }a=0 \\
N_{a-1,t-1} e^{Z_{a-1}}, & \text{if }0<a \leq a_{max}
\end{cases}
$$

###Catch C of age *a* in time *t*

$$C_{a,t} = \frac{F_a}{Z_a}N_{a,t}(1-e^{-Z_a}) $$


```{r Generate Population Data}
N_at[1,1] = R0

for (t in 2:NumYears){
  
  for (a in 1:17){
  
  #  Set inital condition in year t = 0 (assumes no fishing)
    N_at[1,a+1] = N_at[1,(a)]*exp(-M)
    
    Recruitment[1] = sum(N_at[1,]*fa*Ma)
    
    Catch[1,] = 0
    
  # Introduce fishing as Va*F  
    N_at[t,a+1] = exp(-M - Va[a]*F)*N_at[(t - 1),(a)]
    
    N_at[t,1] = Recruitment[t - 1]/(BHa + BHb*Recruitment[t - 1])
    
    Recruitment[t] = sum(N_at[t,]*fa*Ma)
    
    #Catch by cohort = number of individual age a in year t - indvid. age a captured in year t
    
     Catch[t,a+1] = N_at[(t),(a+1)]*(1 - exp(-M - Va[a+1]*F))
    
     Catch[t,1] = 0
    
  }
}
```

```{r ugly_plot_N}

df.hist = stack(N_at[NumYears, ])

barplot(df.hist$values, names.arg = df.hist$ind)

CatchCurve <- lm(log(values) ~ ind, data = df.hist)

Z.est = -CatchCurve$coefficients[2]

print(Z.est)
```


```{r Revenue}

#Calculate Revenue by commercial class------

for (t in 1:NumYears){

  Revenue[t,1] = sum(Weight[1:2]*Catch[t,1:2]*Price[1])
  
  Revenue[t,2] = sum(Weight[3:5]*Catch[t,3:5]*Price[2])
  
  Revenue[t,3] = sum(Weight[5:max(Age)]*Catch[t,5:max(Age)]*Price[3])
  
  Revenue[t,4] = sum(Revenue[t,1:3])
  
}
```


```{r ugly_plot_Rev}
print(Revenue$total[NumYears])

plot(Revenue$total, xlab = "time", ylab = 'Revenue')

```

