---
title: "Varying Length of Seasonal Closure (Constant F and Lc from 2012)"
author: "Alex Smith"
date: "February 5, 2017"
output: html_document
---


Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- instantaneous natural mortality  
 *F* - instantaneous fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())

library(colorRamps)
library(tidyverse)

sapply(list.files(pattern="[.]R$", path="./Functions", full.names=TRUE), source)

#Set Model----
NumYears = 25

R0 = 1000

Z.2012 = 0.579336

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  
maxAge = 18

#Length (cm) at which a fish is 50/95 percent likely to be mature
m50 = 55

m95 = 62.7

#Natural mortality
M <- K * 1.5


#Steepness parameter h - when you dont have a study use 0.7
h=0.7
```



```{r Data}
#Morphology ----

#Our max age is 18 years
Age <- seq(1,maxAge,1)

#Length at median age 
Length <- Linf*(1-exp(-K*((Age + 0.5)-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb



#Maturity
Ma = 1/(1 + exp(-log(19)*((Length - m50)/(m95 - m50))))

#realitve fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)

```


```{r Data Structures}



# Stores abundance in each age cohort

N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))  
  colnames(N_at) = as.character(c(Age))
  
month_N_at <- data.frame(matrix(data = NA, ncol = maxAge, nrow = 12)) 
  colnames(month_N_at) = as.character(c(Age))   

# Stores number of total eggs produced in each year   
Eggs <- vector(length = NumYears)

unfished = vector(length = maxAge)

# Sum of abundance_a * weight_a
Biomass <- vector(length = NumYears)

# Stores output of Baranov catch equation summed across cohorts
Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears)) 
  colnames(Catch) = as.character(c(Age,'Total'))

  
Catch.monthly <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = 12)) 
  colnames(Catch.monthly) = as.character(c(Age,'Year.Total'))  
  
# Groups biomass by commercial class multiples by price_cc and sums in each year
Revenue <- data.frame(matrix(data = NA, ncol = 4, nrow = NumYears)) 
  colnames(Revenue) = c('small',
                        'med',
                        'large')
                        # ,
                        # 'total')

RevenueTotal = vector(length = NumYears) 

Profit = vector(length = NumYears)

CatchTotal = vector(length = NumYears)  
  
# Stores year

year = vector(length = NumYears)

F.Mortality = vector(length = NumYears)

```
  
```{r set_scenario}

#Scenario control-----

#Length at first capture
Lc = 32

Z = Z.2012

seasonal.grid = data.frame(one = c(0, rep(1, 11)),
                       two = c(0,0, rep(1, 10)),
                       three = c(0,0,0, rep(1, 9)), 
                       four = c(0,0,0,0, rep(1, 8)),
                       five = c(0,0,0,0,0, rep(1,7)), 
                       six = c(rep(0, 6), rep(1,6)),
                       seven = c(rep(0,7), rep(1,5) ),
                       eight = c(rep(0,8), rep(1,4)),
                       nine = c(rep(0,9), rep(1,3)),
                       ten = c(rep(0,10), 1, 1), 
                       eleven = c(rep(0,11), 1)) 
                          
Scenarios = gather(seasonal.grid, months, c)

open = vector(length = 12)  
  
  # expand.grid(Lc, Z) %>%
  #           mutate(Label = as.vector(outer(Lc, Z, paste, sep = "-"))) %>%
  #           select(Label , Z = Var2, Lc = Var1) 


InitialCondition <- c(497.3195, 384.9299, 252.3379,141.6849,79.56998,44.69591,25.11237,14.11297,7.933598,4.461228,2.50948,1.41212,0.7949381,0.4476985,0.2522591,0.1422124,0.08021953, 0.1042105)
```

  
```{r run_model}


Model.full = plyr::ddply(Scenarios, 'months', function(x) {
  
  R0. = R0
  maxAge. = maxAge
  h. = h
  fa. = fa
  Ma. = Ma
  Length. = Length
  Weight. = Weight
  M. = M
  
  
  Mseasonal = M. / 12
  
#F converted to monthly
  
  F = (Z.2012 - M) / 12
  
  F2012 = Z.2012 - M
  
  Lc = Lc
  
  # track model progress
  print(paste("F", F, sep = " = "))
  
  print(paste("Lc", Lc, sep = " = "))
  
  print(x$months[1])
  
  #Pristine Inital condition----    
  
  # R0 <- unfished recruits
  unfished[1] = R0.
  # 
  # 
  # estimate age structure of unfished pop
  for (a in 2:(maxAge.)) {
    unfished[a] = unfished[ (a - 1)] * exp(-M.)
    
  }
  
  
  #Overfished Inital condition-----
  N_at[1,] = InitialCondition
  
  Biomass[1] = sum(N_at[1, 1:maxAge.] * Weight.)
  
  #Length (cm) at which a fish is vulnerable to fishing mortality----
  Va = ifelse(Length < Lc, 0, 1)
  
  #Eggs produced in year 1
  Eggs[1] = sum(N_at[1, ] * fa. * Ma.)
  
  phi <- sum(unfished * fa. * Ma.)
  

  Catch[1,] = (((Va * F2012) / (Va * F2012 + M)) * N_at[1, ] * (1 - exp(-M - Va * F2012)))*(Weight/1000)
  
  CatchTotal[1] = sum(Catch[1, 1:maxAge])
  
  # no revenue in year 1
  Revenue[1, 1] = sum(Catch[1, 1:2] * Price[1] )
  
  Revenue[1, 2] = sum( Catch[1, 3:4] * Price[2] )
  
  Revenue[1, 3] = sum(Catch[1, 5:maxAge.] * Price[3] )
  
  RevenueTotal[1] = sum(Revenue[1, 1:3])
  
  #Estimate marginal cost
  
  c = RevenueTotal[1] / F2012
  
 
  open = x$c


  
########################################################################  
  
  for (t in 2:NumYears) {
    
    year[t] = t - 1 
    
    #Beverton-Holt spawner recruit relationship-----
    
    N_at[t, 1] = (0.8 * R0. * h. * Eggs[t - 1]) / (0.2 * phi * (1 - h.) + (h. - 0.2) * Eggs[t - 1])

    
    # monthly survival and catch ---- 
    
    for (m in 2:12) {
      

        # Introduce fishing as Va*F
        
        
        month_N_at[1, ] = exp(-Mseasonal - Va * F*open[1]) * N_at[(t - 1), ]
        
        
        
        month_N_at[m, ] = exp(-Mseasonal - Va * F*open[m]) * month_N_at[(m - 1), ]
        

        
        Catch.monthly[m, ] = (((Va * F*open[m]) / (Va * F*open[m] + Mseasonal)) * month_N_at[m, ] * (1 - exp(-Mseasonal - Va * F*open[m])))*(Weight/1000)
        
        
        Catch[1, ] = 0
        
    }
    
    #store results----
 # Annual abundance
    
    N_at[t, ] = lag(month_N_at[12, ])
    
    plusGroup = month_N_at[12, maxAge] + month_N_at[12, maxAge - 1]
        
    N_at[t, maxAge] = plusGroup
  
 # Annual catch       
    Catch[t, ] = colSums(Catch.monthly)
    
    CatchTotal[t] = sum(Catch[t, 1:maxAge])
    
       
    # Calculate Egg production for time t----  
    Eggs[t] = sum(N_at[t, ] * fa * Ma)
    
    #Calculate Revenue by commercial class ------
    
    Revenue[t, 1] = sum(Catch[t, 1:2] * Price[1] )
    
    Revenue[t, 2] = sum( Catch[t, 3:4] * Price[2] )
    
    Revenue[t, 3] = sum(Catch[t, 5:maxAge.] * Price[3] )
    
    RevenueTotal[t] = sum(Revenue[t, 1:3])
    
    Biomass[t] <- sum(N_at[t, 1:maxAge.] * Weight.)
    
    Profit[t] = RevenueTotal[t] - c*F
    
  }
  
  print("got here")
  
  Months.closed = x$months[1]
  
  Out = cbind(Months.closed, year, N_at, CatchTotal, RevenueTotal, Biomass, Profit)
  
  return(Out)
})


```


```{r NPV}

NPV_effort = Model.full %>%
            group_by(F.Mortality) %>%
            summarise(NPV = sum(PresentValue(Profit, discount = 0.05, year)))

ggplot(NPV_effort, aes(F.Mortality, NPV )) +
  geom_point() +
  theme_minimal()
```

```{r}
F_opt = NPV_effort$F.Mortality[which.max(NPV_effort$NPV)]

Model.full %>%
  filter(F.Mortality == F_opt) %>%
  mutate(PV = PresentValue(Profit, discount = 0.05, year)) %>%
  ggplot(aes(x= year, y = PV)) + 
  geom_point() + 
  theme_minimal() + 
  labs(y = "Discount Profit from Corvina Reina fishery")
```

