---
title: "Control File"
author: "Alex Smith"
date: "2/20/2017"
output: html_document
---


Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- instantaneous natural mortality  
 *F* - instantaneous fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())

library(colorRamps)
library(tidyverse)

sapply(list.files(pattern="[.]R$", path="./Functions", full.names=TRUE), source)

IC <- read.csv('IC.csv')

#Set Model----
NumYears = 25

R0 = 1000

Z.2012 = 0.576057

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  
maxAge = 18

#Length (cm) at which a fish is 50/95 percent likely to be mature
m50 = 55

m95 = 62.7

females = 0.6

#Natural mortality
M <- K * 1.5


#Steepness parameter h - when you dont have a study use 0.7
h=0.7
```



```{r Data}
#Morphology ----

#Our max age is 18 years
Age <- seq(1,maxAge,1)

#Length at median age 
Length <- Linf*(1-exp(-K*((Age + 0.5)-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb



#Maturity
Ma = 1/(1 + exp(-log(19)*((Length - m50)/(m95 - m50))))

#realitve fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)

```


```{r Data Structures}



# Stores abundance in each age cohort

N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))  
  colnames(N_at) = as.character(c(Age))
  
month_N_at <- data.frame(matrix(data = NA, ncol = maxAge, nrow = 12)) 
  colnames(month_N_at) = as.character(c(Age))   

# Stores number of total eggs produced in each year   
Eggs <- vector(length = NumYears)

unfished = vector(length = maxAge)

# Sum of abundance_a * weight_a
Biomass <- vector(length = NumYears)

# Stores output of Baranov catch equation summed across cohorts
Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears)) 
  colnames(Catch) = as.character(c(Age,'Total'))

  
Catch.monthly <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = 12)) 
  colnames(Catch.monthly) = as.character(c(Age,'Year.Total'))  
  
# Groups biomass by commercial class multiples by price_cc and sums in each year
Revenue <- data.frame(matrix(data = NA, ncol = 4, nrow = NumYears)) 
  colnames(Revenue) = c('small',
                        'med',
                        'large')
                        # ,
                        # 'total')

RevenueTotal = vector(length = NumYears) 

Profit = vector(length = NumYears)

CatchTotal = vector(length = NumYears)  
  
# Stores year

year = vector(length = NumYears)

F.Mortality = vector(length = NumYears)

Selectivity = vector(length = NumYears)

```
  
```{r effort_scenario}

#Scenario control-----
Lc = c(32)

Z = c(Z.2012, seq(M , 0.7, 0.001))

Scenarios.effort = expand.grid(Lc, Z) %>%
                    mutate(Label = as.vector(outer(Lc, Z, paste, sep = "-"))) %>%
                    select(Label , Z = Var2, Lc = Var1) %>%
                    mutate(months.open = 12)




InitialCondition <- IC[1,]
  #c(497.3195, 384.9299, 252.3379,141.6849,79.56998,44.69591,25.11237,14.11297,7.933598,4.461228,2.50948,1.41212,0.7949381,0.4476985,0.2522591,0.1422124,0.08021953, 0.1042105)
```


```{r}

Effort = plyr::ddply(Scenarios.effort, 'Label', map_df(.f =Model_fun(Z,Lc,months.open)))

Effort = plyr::ddply(Scenarios.effort, 'Label', function(x){
  return(Model_fun(x$Z, x$Lc, x$months.open))
})




Model_fun(Scenarios.effort.test$Z, Scenarios.effort.test$Lc, Scenarios.effort.test$months.open)

```

