---
title: "Control File"
author: "Alex Smith"
date: "2/20/2017"
output: html_document
---


Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- instantaneous natural mortality  
 *F* - instantaneous fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
#rm(list=ls())

library(colorRamps)
library(tidyverse)

sapply(list.files(pattern="[.]R$", path="./Functions", full.names=TRUE), source)

IC <- read.csv('IC.csv')

# Set Model----
NumYears = 21

# Estimated virgin abundance of 1 yr olds    
  R0 = 355770 
  
# Estimated instananeous mortality in 2012 Zone 201  
  Z.2012 = 0.576057

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  
maxAge = 18

#Length (cm) at which a fish is 50/95 percent likely to be mature
m50 = 55

m95 = 62.7

females = 0.6

#Natural mortality
M <- K * 1.5


#Steepness parameter h - when you dont have a study use 0.7
h=0.7
```



```{r Data}
#Morphology ----

#Our max age is 18 years
Age <- seq(1,maxAge,1)

#Length at median age 
Length <- Linf*(1-exp(-K*((Age + 0.5)-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb



#Maturity
Ma = 1/(1 + exp(-log(19)*((Length - m50)/(m95 - m50))))

#realitve fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)

```


```{r Data Structures}



# Stores abundance in each age cohort

N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))  
  colnames(N_at) = as.character(c(Age))
  
month_N_at <- data.frame(matrix(data = NA, ncol = maxAge, nrow = 12)) 
  colnames(month_N_at) = as.character(c(Age))   

# Stores number of total eggs produced in each year   
Eggs <- vector(length = NumYears)

unfished = vector(length = maxAge)

# Sum of abundance_a * weight_a
Biomass <- vector(length = NumYears)

# Stores output of Baranov catch equation summed across cohorts
Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears)) 
  colnames(Catch) = as.character(c(Age,'Total'))

  
Catch.monthly <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = 12)) 
  colnames(Catch.monthly) = as.character(c(Age,'Year.Total'))  
  
# Groups biomass by commercial class multiples by price_cc and sums in each year
Revenue <- data.frame(matrix(data = NA, ncol = 4, nrow = NumYears)) 
  colnames(Revenue) = c('small',
                        'med',
                        'large')
                        # ,
                        # 'total')

RevenueTotal = vector(length = NumYears) 

Profit = vector(length = NumYears)

CatchTotal = vector(length = NumYears)  
  
# Stores year

year = vector(length = NumYears)

F.Mortality = vector(length = NumYears)

Selectivity = vector(length = NumYears)

```
  
### Effort  
  
  
```{r effort_scenario}

#Scenario control-----
Lc = c(32)

Z = c(Z.2012, seq(M , 0.7, 0.001))

Scenarios.effort = expand.grid(Lc, Z) %>%
                    mutate(Label = as.vector(outer(Lc, Z, paste, sep = "-"))) %>%
                    select(Label , Z = Var2, Lc = Var1) %>%
                    mutate(months.open = 12, closure = 0)




InitialCondition <- IC[1,]
  #c(497.3195, 384.9299, 252.3379,141.6849,79.56998,44.69591,25.11237,14.11297,7.933598,4.461228,2.50948,1.41212,0.7949381,0.4476985,0.2522591,0.1422124,0.08021953, 0.1042105)
```



```{r}


Effort = plyr::ddply(Scenarios.effort, 'Label', function(x) {
  
  return(Model_fun(c(x$Z, x$Lc, x$months.open, x$closure)))

  })


```


```{r write_effort}
write.csv(Effort, "./data/Model_Output/Out_Effort.csv")
```


### Selectivity 

```{r selectivity_scenario}

#Scenario control-----

#Length at first capture
Lc = trunc(Length) #seq(15,122, 1)  #c(29, 31, 30, 38, 45, 62, 70, 76, 101)

Z = Z.2012

Scenarios.selectivity = expand.grid(Lc, Z) %>%
            mutate(Label = as.vector(outer(Lc, Z, paste, sep = "-"))) %>%
            select(Label , Z = Var2, Lc = Var1) %>%
            mutate(months.open = 12, closure = 0)

InitialCondition <- selectivity_opt[,7:24]#IC[1,]
```



```{r}


Selectivity = plyr::ddply(Scenarios.selectivity, 'Label', function(x) {
  
  return(Model_fun(c(x$Z, x$Lc, x$months.open, x$closure)))

  })



NPV_selectivity = selectivity %>%
            group_by(Selectivity) %>%
            summarise(NPV = sum(PresentValue(Profit, discount = 0.09, year)))

```


```{r write_select}
write.csv(Selectivity, "./data/Model_Output/Out_Selectivity.csv")
```



### Seasonal


```{r set_scenario}

#Scenario control-----

#Length at first capture
Lc = 32

Z = Z.2012

months.open = seq(1,12,1)

Scenarios.seasonal = expand.grid(Lc, Z, months.open) %>%
                        select(Z = Var2, Lc = Var1, months.open = Var3) %>%
                        mutate(Label = paste(months.open, Z, Lc, sep = "-")) %>%
                        mutate( closure = 0)



InitialCondition <- IC[1,]
  #c(497.3195, 384.9299, 252.3379,141.6849,79.56998,44.69591,25.11237,14.11297,7.933598,4.461228,2.50948,1.41212,0.7949381,0.4476985,0.2522591,0.1422124,0.08021953, 0.1042105)
```


```{r run_seasonal}


Seasonal = plyr::ddply(Scenarios.seasonal, 'Label', function(x) {
  
  return(Model_fun(c(x$Z, x$Lc, x$months.open, x$closure)))

  })


```



```{r write_season}
write.csv(Seasonal, "./data/Model_Output/Out_Seasonal.csv")
```


```{r set_closer}

#Scenario control-----

#Length at first capture
Lc = 32

Z = Z.2012

months.open = 12

closure = seq(1,21,1)

Scenarios.closure = expand.grid(Lc, Z, months.open, closure) %>%
                        select(Z = Var2, Lc = Var1, months.open = Var3) %>%
                        mutate(Label = paste(closure, Z, Lc, sep = "-")) %>%
                        mutate( closure = closure)



InitialCondition <- IC[1,]
  #c(497.3195, 384.9299, 252.3379,141.6849,79.56998,44.69591,25.11237,14.11297,7.933598,4.461228,2.50948,1.41212,0.7949381,0.4476985,0.2522591,0.1422124,0.08021953, 0.1042105)
```


```{r run_closure}


Closure = plyr::ddply(Scenarios.closure, 'Label', function(x) {
  
  return(Model_fun(c(x$Z, x$Lc, x$months.open, x$closure)))

  })


```



```{r write_season}
write.csv(Closure, "./data/Model_Output/Out_Closure.csv")
```
### Combined


```{r combined_scenario}

#Scenario control-----

#Length at first capture

Lc = trunc(Length)

Z = c(Z.2012, seq((M + 0.025) , 0.8, 0.002) )

months.open = c(3:12)

Scenarios.combined = expand.grid(Lc, Z, months.open) %>%
            select(Z = Var2, Lc = Var1, months.open = Var3) %>%
            mutate(Label = paste( months.open, Z, Lc, sep = "-")) %>%
            mutate( closure = 0)
            


InitialCondition <- IC[1,]
  #c(497.3195, 384.9299, 252.3379,141.6849,79.56998,44.69591,25.11237,14.11297,7.933598,4.461228,2.50948,1.41212,0.7949381,0.4476985,0.2522591,0.1422124,0.08021953, 0.1042105)
```

```{r run_combined}


Combined = plyr::ddply(Scenarios.combined, 'Label', function(x) {
  
  return(Model_fun(c(x$Z, x$Lc, x$months.open, x$closure)))

  })


```
