---
title: "Vary F holding 2012 Lc values"
author: "Alex Smith"
date: "February 5, 2017"
output: html_document
---


Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- natural mortality  
 *F* - fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())

library(colorRamps)
library(tidyverse)

sapply(list.files(pattern="[.]R$", path="./Functions", full.names=TRUE), source)

#Set Model----
NumYears = 25

R0 = 1000

Z.2012 = 0.579336

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  
maxAge = 18

#Length (cm) at which a fish is 50/95 percent likely to be mature
m50 = 55

m95 = 62.7

#Proportion of Stock that is female
females = 0.6

#Natural mortality
M <- K * 1.5


#Steepness parameter h - when you dont have a study use 0.7
h=0.7
```



```{r Data}
#Morphology ----

#Our max age is 18 years
Age <- seq(1,maxAge,1)

#Length at median age 
Length <- Linf*(1-exp(-K*((Age + 0.5)-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb



#Maturity
Ma = 1/(1 + exp(-log(19)*((Length - m50)/(m95 - m50))))

#realitve fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)

```


```{r Data Structures}



# Stores abundance in each age cohort

N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))  
  colnames(N_at) = as.character(c(Age))

# Stores number of total eggs produced in each year   
Eggs <- vector(length = NumYears)

unfished = vector(length = maxAge)

# Sum of abundance_a * weight_a
Biomass <- vector(length = NumYears)

# Stores output of Baranov catch equation summed across cohorts
Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears)) 
  colnames(Catch) = as.character(c(Age,'Total'))

# Groups biomass by commercial class multiples by price_cc and sums in each year
Revenue <- data.frame(matrix(data = NA, ncol = 4, nrow = NumYears)) 
  colnames(Revenue) = c('small',
                        'med',
                        'large')
                        # ,
                        # 'total')

RevenueTotal = vector(length = NumYears) 

Profit = vector(length = NumYears)

CatchTotal = vector(length = NumYears)  
  
# Stores year

year = vector(length = NumYears)

F.Mortality = vector(length = NumYears)

```
  
```{r set_scenario}

#Scenario control-----

#Length at first capture
Lc = c(32)

Z = seq(M , 0.8, 0.025)

Scenarios = expand.grid(Lc, Z) %>%
            mutate(Label = as.vector(outer(Lc, Z, paste, sep = "-"))) %>%
            select(Label , Z = Var2, Lc = Var1)




InitialCondition <- c(497.3195, 384.9299, 252.3379,141.6849,79.56998,44.69591,25.11237,14.11297,7.933598,4.461228,2.50948,1.41212,0.7949381,0.4476985,0.2522591,0.1422124,0.08021953, 0.1042105)
```

  
```{r run_model}

# Scenarios
# 
# replicate(10, yourCoolModel(Scenarios))
# 
# yourCoolModel(Scenarios){
#   random.mort = rnorm(1, mean = .2, .005)
#   return(plyr::ddply(Scenarios, 'Label', function(x))
# }
# 

# random.mort = rnorm(10, mean = .2, .005)
# random.mort = rnorm(1, mean = .2, .005)
# random.length = rnorm(10, mean = .2, .005)
# random.weight = rnorm(10, mean = 10, 20)
# label = 1:10
# test.df = data.frame(random.mort, random.length, random.weight, label)
# 
# sum.col = function(x,y,q){
#   return(x+y + q)
# }
# 
# test.out = plyr::ddply(test.df, 'label', function(x){
#   return(x$random.mort + x$random.length)
#   
# })
# 
# test.out2 = plyr::ddply(test.df, "label", summarise, random.mort+random.length)
# 
# 
# test.out3 = plyr::ddply(test.df, "label", summarise, sum.col(random.mort,random.length, 3))
# 
# 


# 
# Scenarios
# plyr::ldply(random.mort,  function(y){
#   
Model.full = plyr::ddply(Scenarios, 'Label', function(x) {
  R0. = R0
  maxAge. = maxAge
  h. = h
  fa. = fa
  Ma. = Ma
  Length. = Length
  Weight. = Weight
  M. = M
  #M. = y
  
  F = x$Z - M
  
  F2012 = Z.2012 - M
  
  Lc = x$Lc
  
  # track model progress
  print(paste("F", F, sep = " = "))
  
  print(paste("Lc", Lc, sep = " = "))
  
  #Pristine Inital condition----
  
  # #this sets top left
  unfished[1] = R0.

  
  # estimate age structure of unfished pop
  for (a in 2:(maxAge.)) {
  
    unfished[a] = unfished[(a - 1)] * exp(-M.)
  
  }

################################################
# INITALIZE MODEL
################################################  
  
  
  #Overfished Inital condition-----
  N_at[1, ] = InitialCondition
  
  Biomass[1] = sum(N_at[1, 1:maxAge.] * Weight.)
  
  #Length (cm) at which a fish is vulnerable to fishing mortality----
  Va = ifelse(Length < Lc, 0, 1)
  
  #Eggs produced in year 1
  Eggs[1] = sum(N_at[1,] * fa. * Ma. * females)
  
  phi <- sum(unfished * fa. * Ma.)
  
  # no catch in year 1
  Catch[1, ] = (((Va * F2012) / (Va * F2012 + M)) * N_at[1,] * (1 - exp(-M - Va * F2012))) * (Weight / 1000)
  
  CatchTotal[1] = sum(Catch[1, 1:maxAge])
  
  # no revenue in year 1
  Revenue[1, 1] = sum(Catch[1, 1:2] * Price[1])
  
  Revenue[1, 2] = sum(Catch[1, 3:4] * Price[2])
  
  Revenue[1, 3] = sum(Catch[1, 5:maxAge.] * Price[3])
  
  RevenueTotal[1] = sum(Revenue[1, 1:3])
  
  #Estimate marginal cost
  
  c = RevenueTotal[1] / F2012
 
################################################
# CALCULATE ANNUAL CATCH AND ABUNDANCE
################################################    
   
  for (t in 2:NumYears) {
  year[t] = t - 1
  
  #Beverton-Holt spawner recruit relationship-----
  
  N_at[t, 1] = (0.8 * R0. * h. * Eggs[t - 1]) / (0.2 * phi * (1 - h.) + (h. - 0.2) * Eggs[t - 1])
  
  
  #Abundance in each cohort----
  
  for (a in 2:(maxAge.)) {
  # Introduce fishing as Va*F
  
  N_at[t, a] = exp(-M. - Va[a - 1] * F) * N_at[(t - 1), (a - 1)]
  
  # Additional calculation for group maxAge
  plusGroup = N_at[t, maxAge] + exp(-M - Va[maxAge] * F) * N_at[(t - 1), (maxAge)]
  
  N_at[t, maxAge] = plusGroup
  
  #Catch by cohort = number of individual age a in year t - indvid. age a captured in year t----
  
  Catch[t, a] = (((Va[a] * F) / (Va[a] * F + M)) * N_at[(t), (a)] * (1 - exp(-M - Va[a] * F))) *
  (Weight[a] / 1000)
  
  Catch[t, 1] = 0
  
  }
  
  #store results----
  
  CatchTotal[t] = sum(Catch[t, 1:maxAge])
  
  
  
  # Calculate Egg production for time t----
  Eggs[t] = sum(N_at[t,] * fa * Ma)
  
  #Calculate Revenue by commercial class-----
  
  Revenue[t, 1] = sum(Catch[t, 1:2] * Price[1])
  
  Revenue[t, 2] = sum(Catch[t, 3:4] * Price[2])
  
  Revenue[t, 3] = sum(Catch[t, 5:maxAge.] * Price[3])
  
  RevenueTotal[t] = sum(Revenue[t, 1:3])
  
  
  # Biomass-----
  
  Biomass[t] <- sum(N_at[t, 1:maxAge.] * Weight.)
  
  # Profit-----
  
  Profit[t] = RevenueTotal[t] - c * F
  
  }
  
  F.Mortality = F
  
  Out = cbind(F.Mortality,
              year,
              N_at,
              CatchTotal,
              RevenueTotal,
              Biomass,
              Profit)
  
  return(Out)
  
})

#})


```


```{r NPV}

NPV_effort = Model.full %>%
            group_by(F.Mortality) %>%
            summarise(NPV = sum(PresentValue(Profit, discount = 0.09, year)))

#pdf("./plots/NPV_effort.pdf")

p = ggplot(NPV_effort, aes(F.Mortality, NPV )) +
      geom_point(size = 3) +
      scale_x_continuous(breaks = c(seq(0,1,0.1))) +
      scale_y_continuous(breaks = c(seq(-15000,17000,5000))) +
      geom_hline(yintercept = 0, alpha =0.5, lty =2) +
      labs(x = "Effort")
  
MyTheme(p)  


#dev.off()
```

```{r}
F_opt = NPV_effort$F.Mortality[which.max(NPV_effort$NPV)]

Model.full %>%
  filter(F.Mortality == F_opt) %>%
  mutate(PV = PresentValue(Profit, discount = 0.09, year)) %>%
  ggplot(aes(x= year, y = PV, group = F.Mortality)) + 
  geom_line(aes(color = F.Mortality)) + 
  theme_minimal() + 
  labs(y = "Discount Profit from Corvina Reina fishery", x = "Year", color = "Effort") 

```

```{r see_all_paths}
p1 = Model.full %>%
  #filter(F.Mortality == F_opt) %>%
  mutate(PV = PresentValue(Profit, discount = 0.09, year)) %>%
  ggplot(aes(x= year, y = PV, group = F.Mortality)) + 
  geom_line(aes(color = F.Mortality)) + 
  theme_minimal() + 
  labs(y = "Discount Profit from Corvina Reina fishery", x = "Year", color = "Effort")  +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank() ,axis.line = element_line(colour = "black")) +
    theme(axis.text.x = element_text(size=17),
          axis.text.y = element_text(size=17),
          axis.title.x = element_text(size=18),
          axis.title.y = element_text(size=18))
  


#pdf("PathAllEffort.pdf")


plotly::ggplotly(p1)
```


```{r write_out_data}

write.csv(Model.full, "./data/Model_Output/Out_Effort.csv")


write.csv(NPV_effort, "./data/Model_Output/NPV_Effort.csv")



```
