Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- natural mortality  
 *F* - fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())

library(colorRamps)
library(tidyverse)

#Set Model----
NumYears = 40

R0 = 1000

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  
maxAge = 18

#Length (cm) at which a fish is 50/95 percent likely to be mature
m50 = 55

m95 = 62.7


#Natural mortality
M <- K * 1.5


# BHa <- 054.6 #this is made up
# 
# BHb <- 0.0089 #this is made up
#Steepness parameter h - when you dont have a study use 0.7
h=0.7
```



```{r Data}
#Morphology ----

#Our max age is 18 years
Age <- seq(1,maxAge,1)

#Length at median age 
Length <- Linf*(1-exp(-K*((Age + 0.5)-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb


#Scenario control-----

#Length at first capture
Lc = seq(20, 90, 10 )

F = seq(0, 0.5 , 0.25) 

#Maturity
Ma = 1/(1 + exp(-log(19)*((Length - m50)/(m95 - m50))))

#realitve fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)
```


```{r Data Structures}
N_at <- data_frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))  
  colnames(N_at) = as.character(c(Age))

Eggs <- vector(length = NumYears)

Catch <- data_frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears)) 
  colnames(Catch) = as.character(c(Age,'Total'))


Revenue <- data_frame(matrix(data = NA, ncol = 4, nrow = NumYears)) 
  colnames(Revenue) = c('small',
                        'med',
                        'large',
                        'total')



#Scenarios based on length at first capture (Lc)


Results  <- data_frame(F, Lc)
  
# 
# TEMP <- data.frame(matrix(data = NA, ncol = max(Age) + 4 , nrow = length(Lc)))
# colnames(TEMP) <- as.character(c('F','Lc', Age,'Total.Catch','Total.Revenue'))
# 
# 
# Results.Rev <- data.frame(matrix(data = NA, ncol = length(F), nrow = length(Lc))) %>%
#            as_data_frame()
# 
# Results.Biomass <- data.frame(matrix(data = NA, ncol = length(F), nrow = length(Lc))) %>%
#            as_data_frame()
# 
# Results <- list(Rev = Results.Rev, Biomass = Results.Biomass) 

```

### Instantaneous mortality (*Z*)
$$Z_a = M + V_aF $$

###Abundance N of age *a* in time *t*

\usepackage{amsmath}
...
...
$$
N_{a,t} =
\begin{cases}
R_t, & \text{if }a=0 \\
N_{a-1,t-1} e^{Z_{a-1}}, & \text{if }0<a \leq a_{max}
\end{cases}
$$

###Catch C of age *a* in time *t*

$$C_{a,t} = \frac{F_a}{Z_a}N_{a,t}(1-e^{-Z_a}) $$


$$ Revenue =\sum_{a=1}^3N_{a} w_{a}P_1 + \sum_{a=4}^6N_{a} w_{a}P_2 + \sum_{a=6}^AN_{a} w_{a}P_3$$

```{r Generate Population Data}


#this sets top left
N_at[1,1] = R0


#  Set inital condition in year t = 0 (assumes no fishing)
for (a in 2:(maxAge)) {
 
  N_at[1,a] = N_at[1,(a-1)]*exp(-M)
  
}



#Length (cm) at which a fish is vulnerable to fishing mortality

for (f in 1:length(F)){

  for (s in 1:length(Lc)) {
    print(F[f])
    
    print(Lc[s])
    
  Va = ifelse(Length < Lc[s], 0, 1)
  
  #Eggs produced in year 1
  Eggs[1] = sum(N_at[1,]*fa*Ma)
  
  phi <- Eggs[1]
  
  Catch[1,] = 0
  
      
      for (t in 2:NumYears) {
  
    # Calculate abundance in year t for a = 1 ----
      N_at[t,1] = (0.8*R0*h*Eggs[t-1])/(0.2*phi*(1-h)+(h-0.2)*Eggs[t-1])
    
     # Calculate abundance in year t for a 2 : MaxAge ----    
          for (a in 2:(maxAge)) {
          
          
          # Introduce fishing as Va*F  
            N_at[t,a] = exp(-M - Va[a-1]*F[f])*N_at[(t - 1),(a - 1)]
          
          # Adjust max age cohort to account for plus group (this way fish do not experience 100% mortality at max age) 
            
            plusGroup = N_at[t,maxAge] + exp(-M - Va[maxAge]*F[f])*N_at[(t - 1),(maxAge)]
            
            N_at[t,maxAge] = plusGroup
            
           #Catch by cohort = number of individual age a in year t - indvid. age a captured in year t
            
             Catch[t,a] = ((Va[a] * F[f]) / (Va[a] * F[f] + M)) * N_at[(t),(a)] * (1 - exp(-M - Va[a] * F[f]))
            
             Catch[t,1] = 0
            
          }
      
       Catch$Total[t] = sum(Catch[t,1:maxAge])  
      
       Eggs[t] = sum(N_at[t,]*fa*Ma)
       
       #Calculate Revenue by commercial class
       
        Revenue[t,1] = sum(Weight[1:2]*Catch[t,1:2]*Price[1]/1000)
        
        Revenue[t,2] = sum(Weight[3:4]*Catch[t,3:4]*Price[2]/1000)
        
        Revenue[t,3] = sum(Weight[5:max(Age)]*Catch[t,5:max(Age)]*Price[3]/1000)
        
        Revenue[t,4] = sum(Revenue[t,1:3])
            
      }
  
  TEMP[s,1] = Lc[s]
  
  TEMP[s,2:19] = N_at[NumYears,]
  
  TEMP[s,20] = Catch$Total[NumYears]
  
  TEMP[s,21] = Revenue$total[NumYears]
  
 Results$Rev[s,f] <- TEMP[s,21]
 
 Results$Biomass[s,f] <- sum(TEMP[s,2:19]*Weight)
 
    }
  

}  


```

