---
title: "Merge two periods of catch data"
author: "Alex Smith"
date: "June 2, 2016"
output: html_document
---

incopesca_catch.csv has monthly catch data (Kg) for every year from 1990-2013 for Guanacaste, Golfo de Nicoya (also "Gulf of Nicoya" ), Quepos, Golfito, Mar Caribe, and Limon. 

Data Source: SECCION DE ESTADISTICA PESQUERA  INCOPESCA, CON INFORMACION PRIMARIA BRINDADA POR LOS PESCADORES
https://www.incopesca.go.cr/publicaciones/estadiscticas/historico/2013.html

catch_pre1990.csv has catch data (metric tons) from 1952-2013 for 

The output is a .csv file "incopesca_catch" in the 'data' folder. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (basename(getwd())!='data_scripts'){
  setwd('data_scripts')
}
#makes sure you are in the right folder

library(dplyr)
library(readxl) 
library(tidyr)
```

```{r cars}
d1=read.csv('./data/incopesca_catch.csv') %>%
  filter(Region=="Golfo de Nicoya") 
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
