Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- natural mortality  
 *F* - fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())


#Set Model----
NumYears = 50

R0 = 10

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  


#Length (cm) at which a fish is  mature

m = 55


#Natural mortality
M <- 0.258

F <- 0.3125

BHa <- 0.546 #this is made up

BHb <- 0.000089 #this is made up

```



```{r Data}

#Our max age is 18 years
Age <- seq(1,18,1)

Length <- Linf*(1-exp(-K*(Age-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb

#Length at first capture
Lc = seq(20, 100, 3 )

#Maturity
Ma = ifelse(Length < m, 0, 1)

#fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)
```


```{r Data Structures}
N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))
colnames(N_at) = as.character(c(Age))

Recruitment <- vector(length = NumYears)

Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears))
colnames(Catch) <- as.character(c(Age,'Total'))
                        

Revenue <- data.frame(matrix(data = NA, ncol = 4, nrow = NumYears))
colnames(Revenue) =c('small',
                     'med',
                     'large',
                     'total')


#Scenarios based on length at first capture (Lc)



Results <- data.frame(matrix(data = NA, ncol = max(Age) + 3 , nrow = length(Lc)))
colnames(Results) <- as.character(c('Lc', Age,'Total.Catch','Total.Revenue'))

```

### Instantaneous mortality (*Z*)
$$Z_a = M + V_aF $$

###Abundance N of age *a* in time *t*

\usepackage{amsmath}
...
...
$$
N_{a,t} =
\begin{cases}
R_t, & \text{if }a=0 \\
N_{a-1,t-1} e^{Z_{a-1}}, & \text{if }0<a \leq a_{max}
\end{cases}
$$

###Catch C of age *a* in time *t*

$$C_{a,t} = \frac{F_a}{Z_a}N_{a,t}(1-e^{-Z_a}) $$


$$ Revenue =\sum_{a=1}^3N_{a} w_{a}P_1 + \sum_{a=4}^6N_{a} w_{a}P_2 + \sum_{a=6}^AN_{a} w_{a}P_3$$

```{r Generate Population Data}



#this sets top left
N_at[1,1] = R0


#  Set inital condition in year t = 0 (assumes no fishing)
for (a in 1:17){
 
  N_at[1,a+1] = N_at[1,(a)]*exp(-M)
  
}



#Length (cm) at which a fish is vulnerable to fishing mortality



for (s in 1:length(Lc)) {
  
Va = ifelse(Length < Lc[s], 0, 1)

#Recruitment in year 1
Recruitment[1] = sum(N_at[1,]*fa*Ma)

Catch[1,] = 0

    
    for (t in 2:NumYears) {
      
    N_at[t,1] = Recruitment[t - 1] / (BHa + BHb*Recruitment[t - 1])
    
        for (a in 1:17) {
        
        
        # Introduce fishing as Va*F  
          N_at[t,a+1] = exp(-M - Va[a]*F)*N_at[(t - 1),(a)]
          
          
          
         #Catch by cohort = number of individual age a in year t - indvid. age a captured in year t
          
           Catch[t,a+1] = ((Va[a+1]*F)/(Va[a+1]*F+M))*N_at[(t),(a+1)]*(1 - exp(-M - Va[a+1]*F))
          
           Catch[t,1] = 0
          
        }
    
     Catch$Total[t] = sum(Catch[t,1:18])  
    
     Recruitment[t] = sum(N_at[t,]*fa*Ma)
     
     #Calculate Revenue by commercial class
     
      Revenue[t,1] = sum(Weight[1:2]*Catch[t,1:2]*Price[1]/1000)
      
      Revenue[t,2] = sum(Weight[3:4]*Catch[t,3:4]*Price[2]/1000)
      
      Revenue[t,3] = sum(Weight[5:max(Age)]*Catch[t,5:max(Age)]*Price[3]/1000)
      
      Revenue[t,4] = sum(Revenue[t,1:3])
          
    }

Results[s,1] = Lc[s]

Results[s,2:19] = N_at[NumYears,]

Results[s,20] = Catch$Total[NumYears]

Results[s,21] = Revenue$total[NumYears]

}
```


```{r}
library(ggplot2)

# Lc.Catch = 
  ggplot(Results, aes(x=Lc, y= Total.Catch)) +
              geom_jitter() +
              labs(x="Gear Selectivity (Length at first capture)", y = "Annual Total Catch at Equilibirum" ) +
              theme_minimal()
          
```


```{r}

# 
# Lc.Rev =
  
  ggplot(Results, aes(x=Lc, y= Total.Revenue)) +
              geom_jitter() +
              labs(x="Gear Selectivity (Length at first capture)", y = "Annual Total Revenue at Equilibirum" ) +
              theme_minimal()
          
```



```{r}



ggplot(Results, aes(x=Lc, y= (Total.Revenue/Total.Catch))) +
              geom_jitter() +
              theme_minimal()
          
```





```{r}


Results$Total.Abundance = apply(Results[2:19],1, sum)
   
ggplot(Results, aes(x=Total.Abundance, y= Total.Catch)) +
              geom_jitter() +
              theme_minimal()
          
```




```{r}
# Revenue$Lc = seq(1:length(Revenue$small)) 
# 
# Revbar = gather(Revenue[, c(1:3,5)],'Size.Class' ,'Revenue', 1:3)
# 
# 
# library(ggplot2)
# 
# 
# ggplot(Revbar, aes(x= Lc, y= Revenue, fill =factor(Size.Class ))) +
#   geom_bar(stat="identity",position = "stack")
# 

#
```

```{r ugly_plot_N}

# df.hist = stack(N_at[NumYears, ])
# 
# barplot(df.hist$values, names.arg = df.hist$ind)
# 
# CatchCurve <- lm(log(values) ~ ind, data = df.hist)
# 
# Z.est = -CatchCurve$coefficients[2]
# 
# print(Z.est)
```


```{r Revenue}

#Calculate Revenue by commercial class------

# for (t in 1:NumYears){
# 
#   Revenue[t,1] = sum(Weight[1:2]*Catch[t,1:2]*Price[1])
#   
#   Revenue[t,2] = sum(Weight[3:5]*Catch[t,3:5]*Price[2])
#   
#   Revenue[t,3] = sum(Weight[5:max(Age)]*Catch[t,5:max(Age)]*Price[3])
#   
#   Revenue[t,4] = sum(Revenue[t,1:3])
#   
# }
```
