Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- natural mortality  
 *F* - fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())


#Set Model----
NumYears = 25

R0 = 1000

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  


#Length (cm) at which a fish is  mature

m = 55


#Natural mortality
M <- 0.258

Fm <- seq(0,1,0.01)
Fm2014 = 0.30

# BHa <- 054.6 #this is made up
# BHb <- 0.0089 #this is made up
#Steepness parameter h - when you dont have a study use 0.7
h=0.7

```



```{r Data}

#Our max age is 18 years
Age <- seq(1,18,1)

Length <- Linf*(1-exp(-K*(Age-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb

#Length at first capture (Lc= 29 cm for 2014)
Lc = 29

#Maturity
Ma = ifelse(Length < m, 0, 1)

#realitve fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)
```


```{r Data Structures}
N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))
colnames(N_at) = as.character(c(Age))

Eggs <- vector(length = NumYears)

Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears))
colnames(Catch) <- as.character(c(Age,'Total'))
                        

Revenue <- data.frame(matrix(data = NA, ncol = 4, nrow = NumYears))
colnames(Revenue) =c('small',
                     'med',
                     'large',
                     'total')


#Scenarios based on length at first capture (Lc)



Results <- data.frame(matrix(data = NA, ncol = max(Age) + 6 , nrow = length(Lc)))
colnames(Results) <- as.character(c('Fm', Age,'Total.Catch','Total.Revenue', 'Total.Biomass', 'Total.Profits', 'SSBR'))

```

### Instantaneous mortality (*Z*)
$$Z_a = M + V_aF $$

###Abundance N of age *a* in time *t*

\usepackage{amsmath}
...
...
$$
N_{a,t} =
\begin{cases}
R_t, & \text{if }a=0 \\
N_{a-1,t-1} e^{Z_{a-1}}, & \text{if }0<a \leq a_{max}
\end{cases}
$$

###Catch C of age *a* in time *t*

$$C_{a,t} = \frac{F_a}{Z_a}N_{a,t}(1-e^{-Z_a}) $$


$$ Revenue =\sum_{a=1}^3N_{a} w_{a}P_1 + \sum_{a=4}^6N_{a} w_{a}P_2 + \sum_{a=6}^AN_{a} w_{a}P_3$$

```{r Generate Population Data}



#this sets top left
N_at[1,1] = R0


#  Set inital condition in year t = 0 (assumes no fishing)
for (a in 1:17){
 
  N_at[1,a+1] = N_at[1,(a)]*exp(-M)
  
}

# Next periods


for (f in 1:length(Fm)) {
  
Va = ifelse(Length < Lc, 0, 1)

#Eggs in year 1
Eggs[1] = sum(N_at[1,]*fa*Ma) # this is equal to pi * R0

phi <- Eggs[1]

Catch[1,] = 0

    
    for (t in 2:NumYears) {
      
    N_at[t,1] =  (0.8*R0*h*(sum(N_at[t-1,]*fa*Ma)))/(0.2*phi*(1-h)+(h-0.2)*(sum(N_at[t-1,]*fa*Ma)))
      
        for (a in 1:17) {
        
        
        # Introduce fishing as Va*F  
          N_at[t,a+1] = exp(-M - Va[a]*Fm[f])*N_at[(t - 1),(a)]
          
          
          
         #Catch by cohort = number of individual age a in year t - indvid. age a captured in year t
          
           Catch[t,a+1] = ((Va[a+1]*Fm[f])/(Va[a+1]*Fm[f]+M))*N_at[(t),(a+1)]*(1 - exp(-M - Va[a+1]*Fm[f]))
          
           Catch[t,1] = 0
          
        }
    
     Catch$Total[t] = sum(Catch[t,1:18]) 
    
     Eggs[t] = sum(N_at[t,]*fa*Ma)
     
     #Calculate Revenue by commercial class
     
      Revenue[t,1] = sum(Weight[1:2]*Catch[t,1:2]*Price[1]/1000)
      
      Revenue[t,2] = sum(Weight[3:4]*Catch[t,3:4]*Price[2]/1000)
      
      Revenue[t,3] = sum(Weight[5:max(Age)]*Catch[t,5:max(Age)]*Price[3]/1000)
      
      Revenue[t,4] = sum(Revenue[t,1:3])
          
    }

Results[f,1] = Fm[f]

Results[f,2:19] = N_at[NumYears,]

Results[f,20] = Catch$Total[NumYears]

Results[f,21] = Revenue$total[NumYears]

Biomass <- t(t(N_at) * Weight)

Results[f, 22] = sum(Biomass[NumYears,])

}

Results[, 23] = Results$Total.Revenue - Results$Total.Revenue[which(Results$Fm == Fm2014)]
Results[, 24] = rowSums(Results[, 2:19]*fa*Ma)


```

```{r plot_revenue}

library(ggplot2)
library(gridExtra)

opt.Fm <- Results$Fm[which.max(Results$Total.Profit)]
slope.costs<- (Results$Total.Revenue[which(Results$Fm==Fm2014)] - 0) /(Fm2014-0)

Fm.Biom= 
  
  ggplot(Results, aes(x=Fm, y= Total.Biomass/1000)) +
   geom_line(col = "darkblue", size = 1.09)+
   geom_vline(xintercept = opt.Fm, col= "chartreuse3", linetype="dashed", size=1.05)+
   geom_vline(xintercept = Fm2014, col= "orange", linetype="dashed", size=1.05)+
   scale_x_continuous(limits=c(min(Fm),max(Fm)), breaks=seq(0, 1, 0.1),  expand= c(0,0)) +
    scale_y_continuous(expand= c(0,0)) +
   labs(x="Fishing mortality", y = "Biomass (Tons)" ) +
   theme_minimal() +            
   theme(axis.title = element_text(size=15, face= "bold"),axis.text = element_text(size=12), panel.grid.major = element_blank(), panel.grid.minor = element_blank() ,axis.line = element_line(colour = "black"))

Fm.SSBR = 

   ggplot(Results, aes(x=Fm, y= SSBR/1000000)) +
   geom_line(se=FALSE, col = "darkblue", size =1.09) +
   geom_vline(xintercept = opt.Fm, col= "chartreuse3", linetype="dashed", size=1.05)+
   geom_vline(xintercept = Fm2014, col= "orange", linetype="dashed", size=1.05)+
   scale_x_continuous(limits=c(min(Fm),max(Fm)), breaks=seq(0, 1, 0.1)) +
   labs(x="Fishing mortality", y = "Eggs production (millions)" ) +
   theme_minimal() +            
   theme(axis.title = element_text(size=15, face= "bold"),axis.text = element_text(size=12), panel.grid.major = element_blank(), panel.grid.minor = element_blank() ,axis.line = element_line(colour = "black"))

Fm.Catch = 

   ggplot(Results, aes(x=Fm, y= Total.Catch)) +
   geom_line(se=FALSE, col = "darkblue", size =1.09) +
   geom_vline(xintercept = opt.Fm, col= "chartreuse3", linetype="dashed", size=1.05)+
   geom_vline(xintercept = Fm2014, col= "orange", linetype="dashed", size=1.05)+
   scale_x_continuous(limits=c(min(Fm),max(Fm)), breaks=seq(0, 1, 0.1)) +
   labs(x="Fishing mortality", y = "Catch (Number of individuals)" ) +
   theme_minimal() +            
   theme(axis.title = element_text(size=15, face= "bold"),axis.text = element_text(size=12), panel.grid.major = element_blank(), panel.grid.minor = element_blank() ,axis.line = element_line(colour = "black"))

Fm.Rev =
  
  ggplot(Results, aes(x=Fm, y= Total.Revenue)) +
   geom_line(col = "darkblue", size = 1.09) +
   geom_vline(xintercept = opt.Fm, col= "chartreuse3", linetype="dashed", size=1.05)+
   geom_vline(xintercept = Fm2014, col= "orange", linetype="dashed", size=1.05)+
   geom_abline(intercept = 0, slope= slope.costs, col= "red", size=1.05)+
   scale_x_continuous(limits=c(min(Fm),max(Fm)), breaks=seq(0, 1, 0.1),  expand= c(0,0)) +
   labs(x="Fishing mortality", y = "Dollars ($)", size= 12) +
   theme_minimal() +   
   theme(axis.title = element_text(size=15, face= "bold"),axis.text = element_text(size=12), panel.grid.major = element_blank(), panel.grid.minor = element_blank() ,axis.line = element_line(colour = "black"))



Fig3<- grid.arrange(Fm.Biom, Fm.Rev,  ncol=2, nrow =1)
Fig4<- grid.arrange(Fm.SSBR, Fm.Catch, ncol=2, nrow =1)
          
          
```



```{r}
#How much revenue and biomass generates the optimal Fm compared to the 2014 Fm?

Diff.Rev <- (max(Results$Total.Revenue)*100)/Results$Total.Revenue[which(Results$Fm== Fm2014)]
Diff.Biomass <- (Results$Total.Biomass[which(Results$Fm==opt.Fm)]*100)/Results$Total.Biomass[which(Results$Fm==Fm2014)]
          
```





```{r}


Results$Total.Abundance = apply(Results[2:19],1, sum)
   
ggplot(Results, aes(x=Total.Abundance, y= Total.Catch)) +
              geom_jitter() +
              theme_minimal()
          
```




```{r}
# Revenue$Lc = seq(1:length(Revenue$small)) 
# 
# Revbar = gather(Revenue[, c(1:3,5)],'Size.Class' ,'Revenue', 1:3)
# 
# 
# library(ggplot2)
# 
# 
# ggplot(Revbar, aes(x= Lc, y= Revenue, fill =factor(Size.Class ))) +
#   geom_bar(stat="identity",position = "stack")
# 

#
```

```{r ugly_plot_N}

# df.hist = stack(N_at[NumYears, ])
# 
# barplot(df.hist$values, names.arg = df.hist$ind)
# 
# CatchCurve <- lm(log(values) ~ ind, data = df.hist)
# 
# Z.est = -CatchCurve$coefficients[2]
# 
# print(Z.est)
```


```{r Revenue}

#Calculate Revenue by commercial class------

# for (t in 1:NumYears){
# 
#   Revenue[t,1] = sum(Weight[1:2]*Catch[t,1:2]*Price[1])
#   
#   Revenue[t,2] = sum(Weight[3:5]*Catch[t,3:5]*Price[2])
#   
#   Revenue[t,3] = sum(Weight[5:max(Age)]*Catch[t,5:max(Age)]*Price[3])
#   
#   Revenue[t,4] = sum(Revenue[t,1:3])
#   
# }
```
