---
title: "trying optim"
author: "Alex Smith"
date: "February 5, 2017"
output: html_document
---


Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- instantaneous natural mortality  
 *F* - instantaneous fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())

library(colorRamps)
library(tidyverse)

sapply(list.files(pattern="[.]R$", path="./Functions", full.names=TRUE), source)

IC <- read.csv('IC.csv')

#Set Model----
NumYears = 25

R0 = 1000

Z.2012 = 0.579336

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  
maxAge = 18

#Length (cm) at which a fish is 50/95 percent likely to be mature
m50 = 55

m95 = 62.7

females = 0.6

#Natural mortality
M <- K * 1.5


#Steepness parameter h - when you dont have a study use 0.7
h=0.7
```



```{r Data}
#Morphology ----

#Our max age is 18 years
Age <- seq(1,maxAge,1)

#Length at median age 
Length <- Linf*(1-exp(-K*((Age + 0.5)-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb



#Maturity
Ma = 1/(1 + exp(-log(19)*((Length - m50)/(m95 - m50))))

#realitve fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)

```


```{r Data Structures}



# Stores abundance in each age cohort

N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))  
  colnames(N_at) = as.character(c(Age))
  
month_N_at <- data.frame(matrix(data = NA, ncol = maxAge, nrow = 12)) 
  colnames(month_N_at) = as.character(c(Age))   

# Stores number of total eggs produced in each year   
Eggs <- vector(length = NumYears)

unfished = vector(length = maxAge)

# Sum of abundance_a * weight_a
Biomass <- vector(length = NumYears)

# Stores output of Baranov catch equation summed across cohorts
Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears)) 
  colnames(Catch) = as.character(c(Age,'Total'))

  
Catch.monthly <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = 12)) 
  colnames(Catch.monthly) = as.character(c(Age,'Year.Total'))  
  
# Groups biomass by commercial class multiples by price_cc and sums in each year
Revenue <- data.frame(matrix(data = NA, ncol = 4, nrow = NumYears)) 
  colnames(Revenue) = c('small',
                        'med',
                        'large')
                        # ,
                        # 'total')

RevenueTotal = vector(length = NumYears) 

Profit = vector(length = NumYears)

CatchTotal = vector(length = NumYears)  
  
# Stores year

year = vector(length = NumYears)

F.Mortality = vector(length = NumYears)

Selectivity = vector(length = NumYears)

```
  
```{r set_scenario}

#Scenario control-----

#Length at first capture
# 
# Lc = c(29, 31, 38, 45, 62, 70, 76, 101)
# 
# Z = seq((M + 0.025) , 0.8, 0.025)
# 
# months.open = c(1:12)
# 
# Scenarios = expand.grid(Lc, Z, months.open) %>%
#             select(Z = Var2, Lc = Var1, months.open = Var3) %>%
#             mutate(Label = paste( months.open, Z, Lc, sep = "-"))
#             
# 
# open = vector(length = 12)  
  
  # expand.grid(Lc, Z) %>%
  #           mutate(Label = as.vector(outer(Lc, Z, paste, sep = "-"))) %>%
  #           select(Label , Z = Var2, Lc = Var1) 



InitialCondition <- IC[1,]
  #c(497.3195, 384.9299, 252.3379,141.6849,79.56998,44.69591,25.11237,14.11297,7.933598,4.461228,2.50948,1.41212,0.7949381,0.4476985,0.2522591,0.1422124,0.08021953, 0.1042105)
```

  
```{r run_model}


Model.fun = function(x) {
  Z = x[1]
  
  Lc = 32
  
  months.open = 12
  
  R0. = R0
  maxAge. = maxAge
  h. = h
  fa. = fa
  Ma. = Ma
  Length. = Length
  Weight. = Weight
  M. = M
  
  
  Mseasonal = M. / 12
  
#F converted to monthly
  
  F = (Z - M) / 12
  
  F2012 = Z.2012 - M
  
  
  # track model progress
  # print(paste("F", F, sep = " = "))
  # 
  # print(paste("Lc", x$Lc, sep = " = "))
  # 
  # print(x$months.open[1])
  
  #Pristine Inital condition----    
  
  # R0 <- unfished recruits
  unfished[1] = R0.
  # 
  # 
  # estimate age structure of unfished pop
  for (a in 2:(maxAge.)) {
    unfished[a] = unfished[ (a - 1)] * exp(-M.)
    
  }
  
  
  #Overfished Inital condition-----
  N_at[1,] = InitialCondition
  
  Biomass[1] = sum(N_at[1, 1:maxAge.] * Weight.)
  
  #Length (cm) at which a fish is vulnerable to fishing mortality----
  Va = ifelse(Length < Lc, 0, 1)
  
  #Eggs produced in year 1
  Eggs[1] = sum(N_at[1, ] * fa. * Ma. * females)
  
  phi <- sum(unfished * fa. * Ma. * females)
  

  Catch[1,] = (((Va * F2012) / (Va * F2012 + M)) * N_at[1, ] * (1 - exp(-M - Va * F2012)))*(Weight/1000)
  
  CatchTotal[1] = sum(Catch[1, 1:maxAge])
  
  # no revenue in year 1
  Revenue[1, 1] = sum(Catch[1, 1:2] * Price[1] )
  
  Revenue[1, 2] = sum( Catch[1, 3:4] * Price[2] )
  
  Revenue[1, 3] = sum(Catch[1, 5:maxAge.] * Price[3] )
  
  RevenueTotal[1] = sum(Revenue[1, 1:3])
  
  #Estimate marginal cost
  
  c = RevenueTotal[1] / F2012
  
 
  open = c(rep(0, (12 - months.open)), rep(1, (months.open)))


  
########################################################################  
  
  for (t in 2:NumYears) {
    
    year[t] = t - 1 
    
    #Beverton-Holt spawner recruit relationship-----
    
    N_at[t, 1] = (0.8 * R0. * h. * Eggs[t - 1]) / (0.2 * phi * (1 - h.) + (h. - 0.2) * Eggs[t - 1])

    
    # monthly survival and catch ---- 
    
    for (m in 2:12) {
      

        # Introduce fishing as Va*F
        
        
        month_N_at[1, ] = exp(-Mseasonal - Va * F*open[1]) * N_at[(t - 1), ]
        
    
        
        month_N_at[m, ] = exp(-Mseasonal - Va * F*open[m]) * month_N_at[(m - 1), ]
        

        
        Catch.monthly[m, ] = (((Va * F* open[m]) / (Va * F*open[m] + Mseasonal)) * month_N_at[m, ] * (1 - exp(-Mseasonal - Va * F*open[m])))*(Weight/1000)
        
        
        Catch.monthly[1, ] = (((Va * F*open[1]) / (Va * F*open[1] + Mseasonal)) * month_N_at[1, ] * (1 - exp(-Mseasonal - Va * F*open[1])))*(Weight/1000)
        
    }
    
    #store results----
 # Annual abundance
    
    N_at[t, 2:maxAge. ] = month_N_at[12, 1:maxAge. -1 ] 
    
    plusGroup = month_N_at[12, maxAge] + month_N_at[12, maxAge - 1]
        
    N_at[t, maxAge] = plusGroup
  
 # Annual catch       
    Catch[t, ] = colSums(Catch.monthly)
    
    CatchTotal[t] = sum(Catch[t, 1:maxAge])
    
       
    # Calculate Egg production for time t----  
    Eggs[t] = sum(N_at[t, ] * fa * Ma * females)
    
    #Calculate Revenue by commercial class ------
    
    Revenue[t, 1] = sum(Catch[t, 1:2] * Price[1] )
    
    Revenue[t, 2] = sum( Catch[t, 3:4] * Price[2] )
    
    Revenue[t, 3] = sum(Catch[t, 5:maxAge.] * Price[3] )
    
    RevenueTotal[t] = sum(Revenue[t, 1:3])
    
    Biomass[t] <- sum(N_at[t, 1:maxAge.] * Weight.)
    
    Profit[t] = RevenueTotal[t] - c*(F)*sum(open)
    
  }
  

  
  Months.closed = 12 - months.open[1]
  
  F.Mortality = F * 12
  
  Selectivity = Lc
  
  Out = cbind(Months.closed, F.Mortality, Selectivity, year, N_at, CatchTotal, RevenueTotal, Biomass, Profit)
  
  
  NPV = (sum(PresentValue(Profit, discount = 0.09, year)))
  
  return(NPV)
}


```


```{r NPV}

optim(0.4, Model.fun, method = "L-BFGS-B", lower = 0.258, upper = 0.8, control = list(maxit = 500, fnscale = -1, factr = 0.003, trace=6))

```


```{r NPV}

optim(c(0.55, 70, 12), Model.fun, method = "L-BFGS-B", lower = c(0.258,29,0), upper = c(0.8,101,12), control = list(maxit = 50000, fnscale = -1, factr = 0.003, parscale = c(0.01, 5 , 1)))

```
```{r}
#Scenario control-----

#Length at first capture

Lc = c(29, 31, 38, 45, 62, 70, 76, 101)

Z = seq((M + 0.025) , 0.8, 0.025)

months.open = c(1:12)

Scenarios = expand.grid(Lc, Z, months.open) %>%
            select(Z = Var2, Lc = Var1, months.open = Var3) %>%
            mutate(Label = paste( months.open, Z, Lc, sep = "-")) %>%
            group_by(Label) %>%
            summarise(NPV = Model.fun(c(Z, Lc, months.open)))


```

