Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- natural mortality  
 *F* - fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())

library(colorRamps)

#Set Model----
NumYears = 40

R0 = 1000

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  


#Length (cm) at which a fish is  mature

m = 55


#Natural mortality
M <- 0.258


# BHa <- 054.6 #this is made up
# 
# BHb <- 0.0089 #this is made up
#Steepness parameter h - when you dont have a study use 0.7
h=0.7
```



```{r Data}

#Our max age is 18 years
Age <- seq(1,18,1)

Length <- Linf*(1-exp(-K*(Age-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb

#Length at first capture
Lc = seq(15, 100, 2 )

F = seq(0,1, 0.025) 

#Maturity
Ma = ifelse(Length < m, 0, 1)

#realitve fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)
```


```{r Data Structures}
N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))
colnames(N_at) = as.character(c(Age))

Eggs <- vector(length = NumYears)

Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears))
colnames(Catch) <- as.character(c(Age,'Total'))
                        

Revenue <- data.frame(matrix(data = NA, ncol = 4, nrow = NumYears))
colnames(Revenue) =c('small',
                     'med',
                     'large',
                     'total')



#Scenarios based on length at first capture (Lc)



TEMP <- data.frame(matrix(data = NA, ncol = max(Age) + 4 , nrow = length(Lc)))
colnames(TEMP) <- as.character(c('F','Lc', Age,'Total.Catch','Total.Revenue'))


Results.Rev <- data.frame(matrix(data = NA, ncol = length(F), nrow = length(Lc)))

Results.Biomass <- data.frame(matrix(data = NA, ncol = length(F), nrow = length(Lc)))

Results <- list(Rev = Results.Rev, Biomass = Results.Biomass)

```

### Instantaneous mortality (*Z*)
$$Z_a = M + V_aF $$

###Abundance N of age *a* in time *t*

\usepackage{amsmath}
...
...
$$
N_{a,t} =
\begin{cases}
R_t, & \text{if }a=0 \\
N_{a-1,t-1} e^{Z_{a-1}}, & \text{if }0<a \leq a_{max}
\end{cases}
$$

###Catch C of age *a* in time *t*

$$C_{a,t} = \frac{F_a}{Z_a}N_{a,t}(1-e^{-Z_a}) $$


$$ Revenue =\sum_{a=1}^3N_{a} w_{a}P_1 + \sum_{a=4}^6N_{a} w_{a}P_2 + \sum_{a=6}^AN_{a} w_{a}P_3$$

```{r Generate Population Data}



#this sets top left
N_at[1,1] = R0


#  Set inital condition in year t = 0 (assumes no fishing)
for (a in 1:17){
 
  N_at[1,a+1] = N_at[1,(a)]*exp(-M)
  
}



#Length (cm) at which a fish is vulnerable to fishing mortality

for (f in 1:length(F)){

  for (s in 1:length(Lc)) {
    print(F[f])
    
    print(Lc[s])
    
  Va = ifelse(Length < Lc[s], 0, 1)
  
  #Eggs produced in year 1
  Eggs[1] = sum(N_at[1,]*fa*Ma)
  
  phi <- Eggs[1]
  
  Catch[1,] = 0
  
      
      for (t in 2:NumYears) {
        
      N_at[t,1] = (0.8*R0*h*Eggs[t-1])/(0.2*phi*(1-h)+(h-0.2)*Eggs[t-1])
      
          for (a in 1:17) {
          
          
          # Introduce fishing as Va*F  
            N_at[t,a+1] = exp(-M - Va[a]*F[f])*N_at[(t - 1),(a)]
            
            
            
           #Catch by cohort = number of individual age a in year t - indvid. age a captured in year t
            
             Catch[t,a+1] = ((Va[a+1]*F[f])/(Va[a+1]*F[f]+M))*N_at[(t),(a+1)]*(1 - exp(-M - Va[a+1]*F[f]))
            
             Catch[t,1] = 0
            
          }
      
       Catch$Total[t] = sum(Catch[t,1:18])  
      
       Eggs[t] = sum(N_at[t,]*fa*Ma)
       
       #Calculate Revenue by commercial class
       
        Revenue[t,1] = sum(Weight[1:2]*Catch[t,1:2]*Price[1]/1000)
        
        Revenue[t,2] = sum(Weight[3:4]*Catch[t,3:4]*Price[2]/1000)
        
        Revenue[t,3] = sum(Weight[5:max(Age)]*Catch[t,5:max(Age)]*Price[3]/1000)
        
        Revenue[t,4] = sum(Revenue[t,1:3])
            
      }
  
  TEMP[s,1] = Lc[s]
  
  TEMP[s,2:19] = N_at[NumYears,]
  
  TEMP[s,20] = Catch$Total[NumYears]
  
  TEMP[s,21] = Revenue$total[NumYears]
  
 Results$Rev[s,f] <- TEMP[s,21]
 
 Results$Biomass[s,f] <- sum(TEMP[s,2:19]*Weight)
 
    }
  

}  


```

```{r heatmap_Revenue}

rownames(Results$Rev) = as.character(Lc)

mat.Revenue = as.matrix(Results$Rev)
colnames(mat.Revenue) = as.character(F)

#heatmaply::heatmaply(mat.Revenue,  xlab = "Fishing Mortality (F)", ylab = "Selectivity")
 


#hm = heatmap(mat.Revenue, Rowv = NA, Colv = NA, labRow = as.character(Lc))

filled.contour(y = F,
               x = Lc,
               z = mat.Revenue,
              col = rev(matlab.like(19)),               
              plot.title = title(main = "Fishing Revenues",
                            xlab = "Gear Selectivity (Length at first capture)", 
                            ylab = "Fishing Pressure (F)"))

```

```{r heatmap_Biomass}

rownames(Results$Biomass) = as.character(Lc)

mat.Biomass = as.matrix(Results$Biomass)
colnames(mat.Biomass) = as.character(F)

#heatmaply::heatmaply(mat.Revenue,  xlab = "Fishing Mortality (F)", ylab = "Selectivity")
 

filled.contour(y = Lc,
               x = F,
               z = t(mat.Biomass),
              col = rev(matlab.like(23)),
              plot.title = title(main = "Biomass at Equilibrium",
                            ylab = "Gear Selectivity (Length at first capture)",
                            xlab = "Effort (Fishing Mortality)"))
#hm = heatmap(mat.Revenue, Rowv = NA, Colv = NA, labRow = as.character(Lc))
# 
# image(y = F,
#                x = Lc,
#                z = mat.Biomass,
#               plot.title = title(main = "Equilibrium Biomass",
#                             xlab = "Gear Selectivity (Length at first capture)", 
#                             ylab = "Fishing Pressure (F)"))
# contour(y = F,
#                x = Lc,
#                z = mat.Revenue, add = TRUE, )

```

```{r eval=FALSE}
library(ggplot2)

# Lc.Catch = 
  ggplot(TEMP, aes(x=Lc, y= Total.Catch)) +
              geom_jitter() +
              labs(x="Gear Selectivity (Length at first capture)", y = "Annual Total Catch at Equilibirum" ) +
              theme_minimal()
          
```


```{r eval=FALSE}

# 
# Lc.Rev =
  
  ggplot(TEMP, aes(x=Lc, y= Total.Revenue)) +
              geom_jitter() +
              labs(x="Gear Selectivity (Length at first capture)", y = "Annual Total Revenue at Equilibirum" ) +
              theme_minimal()
          
```



```{r schaffer_plot}

Actual.Rev = t(Results$Rev[5,])

schaffer.data <- data.frame(mortality = F, 
                            revenue = Actual.Rev)

colnames(schaffer.data) <- c("mortality", "revenue")

c = schaffer.data[13,2]/schaffer.data[13,1]

ggplot(schaffer.data, aes(x = mortality, y = revenue )) +
              geom_point(color="darkblue") +
              geom_line(color="darkblue", size=1, show.legend = TRUE) +
              #geom_smooth(se =FALSE) +
              geom_vline(xintercept = schaffer.data[13,1], lty = 2) +
              geom_hline(yintercept = schaffer.data[13,2], lty = 2) +
              geom_abline(intercept = 0 , slope = c, color = "red", , size=1, show.legend = TRUE) +
              labs(x = "Effort (fishing mortality)", y = "Dollars") +
              theme_minimal() +
              theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
          
```





```{r heatmap_profit}

Costs = c*F

Results$Profit <- apply(Results$Rev , 1, '-', Costs)


 lvls <- seq(min(Results$Profit), max(Results$Profit), length.out = 70)

filled.contour(x = F,
               y = Lc,
               z = Results$Profit,
               col = rev(matlab.like(15)),
               #levels=lvls,
               plot.title = title(main = "Profit",
                            ylab = "Gear Selectivity (length at first capture)", 
                            xlab = "Effort (Fishing Mortality)"))


```




```{r}
# Revenue$Lc = seq(1:length(Revenue$small)) 
# 
# Revbar = gather(Revenue[, c(1:3,5)],'Size.Class' ,'Revenue', 1:3)
# 
# 
# library(ggplot2)
# 
# 
# ggplot(Revbar, aes(x= Lc, y= Revenue, fill =factor(Size.Class ))) +
#   geom_bar(stat="identity",position = "stack")
# 

#
```

```{r ugly_plot_N}

# df.hist = stack(N_at[NumYears, ])
# 
# barplot(df.hist$values, names.arg = df.hist$ind)
# 
# CatchCurve <- lm(log(values) ~ ind, data = df.hist)
# 
# Z.est = -CatchCurve$coefficients[2]
# 
# print(Z.est)
```


```{r Revenue}

#Calculate Revenue by commercial class------

# for (t in 1:NumYears){
# 
#   Revenue[t,1] = sum(Weight[1:2]*Catch[t,1:2]*Price[1])
#   
#   Revenue[t,2] = sum(Weight[3:5]*Catch[t,3:5]*Price[2])
#   
#   Revenue[t,3] = sum(Weight[5:max(Age)]*Catch[t,5:max(Age)]*Price[3])
#   
#   Revenue[t,4] = sum(Revenue[t,1:3])
#   
# }
```
