Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- natural mortality  
 *F* - fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())

library(colorRamps)
library(tidyverse)

#Set Model----
NumYears = 40

R0 = 1000

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  
maxAge = 18

#Length (cm) at which a fish is 50/95 percent likely to be mature
m50 = 55

m95 = 62.7

#Natural mortality
M <- K * 1.5


#Steepness parameter h - when you dont have a study use 0.7
h=0.7
```



```{r Data}
#Morphology ----

#Our max age is 18 years
Age <- seq(1,maxAge,1)

#Length at median age 
Length <- Linf*(1-exp(-K*((Age + 0.5)-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb


#Scenario control-----

#Length at first capture
Lc = seq(20, 60, 10 )

F = seq(0, 0.5 , 0.25) 


#Maturity
Ma = 1/(1 + exp(-log(19)*((Length - m50)/(m95 - m50))))

#realitve fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)
```


```{r Data Structures}

Scenarios = expand.grid(Lc, F) %>%
            mutate(Label = as.vector(outer(Lc, F, paste, sep = "-"))) %>%
            select(Label , F = Var2, Lc = Var1) 

# %>%
#             split(.$Label)

# maybe = tribble(~Label, ~Scenarios)

#  Out = data.frame(matrix(data = NA, ncol = 2, nrow = 2))
# 
#  
#  
#  
# testfun = function(F, Lc){
#   
# F + Lc
#  
# #  Out[1,1] = F + Lc
# #  
# #  Out[1,2] = F + Lc + 1
# #  
# # Out[2,1] = F - Lc
# #  
# #  Out[2,2] = F - Lc + 1
# #  
# #  return(Out)
#   
# }
# 
# test = Scenarios %>%
#     group_by(F) %>%
#   nest()
# 
# result = test %>%
#   


N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))  
  colnames(N_at) = as.character(c(Age))

Eggs <- vector(length = NumYears)

Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears)) 
  colnames(Catch) = as.character(c(Age,'Total'))


Revenue <- data_frame(matrix(data = NA, ncol = 4, nrow = NumYears)) 
  colnames(Revenue) = c('small',
                        'med',
                        'large',
                        'total')



#Scenarios based on length at first capture (Lc)


Results  <- data_frame(F, Lc)
  
# 
# TEMP <- data.frame(matrix(data = NA, ncol = max(Age) + 4 , nrow = length(Lc)))
# colnames(TEMP) <- as.character(c('F','Lc', Age,'Total.Catch','Total.Revenue'))
# 
# 
# Results.Rev <- data.frame(matrix(data = NA, ncol = length(F), nrow = length(Lc))) %>%
#            as_data_frame()
# 
# Results.Biomass <- data.frame(matrix(data = NA, ncol = length(F), nrow = length(Lc))) %>%
#            as_data_frame()
# 
# Results <- list(Rev = Results.Rev, Biomass = Results.Biomass) 

a = c(1,2,3)
b = c(4,5,6)

c = expand.grid(a,b)

testfun = function(input){
  return(data.frame(matrix(data = input, ncol = 3, nrow = 3)))
}


testfun(1)
testfun(2)

plyr::ldply(a, testfun)
testBest =plyr::ddply(c, c('Var1', 'Var2'), function(x){
  
  return(data.frame(matrix(data = x$Var1, ncol = 3, nrow = x$Var2)))
})


```

```{r hopeful}


PlzWork = plyr::ddply(Scenarios,'Label', function(x){ 
  
  R0. = R0 
  maxAge. = maxAge 
  h. = h
  fa. = fa
  Ma. = Ma
  Length. = Length
  Weight. = Weight
  M. = M
  
  F = x$F
  
  Lc = x$Lc
  
  #this sets top left
  N_at[1,1] = R0.
  
  
  #  Set inital condition in year t = 0 (assumes no fishing)
  for (a in 2:(maxAge.)) {
    
    N_at[1,a] = N_at[1,(a-1)]*exp(-M.)
    
  }
  
  
  
  #Length (cm) at which a fish is vulnerable to fishing mortality
  
  print(F)
  
  print(Lc)
  
  Va = ifelse(Length. < Lc, 0, 1)
  
  #Eggs produced in year 1
  Eggs[1] = sum(N_at[1,]*fa.*Ma.)
  
  phi <- Eggs[1]
  
  #Catch[1,] = 0
  
  
  for (t in 2:NumYears) {
    
    N_at[t,1] = (0.8 * R0. * h. * Eggs[t-1]) / (0.2 * phi * (1-h.) + (h.-0.2) * Eggs[t-1])
    
    for (a in 2:(maxAge.)) {
      
      
      # Introduce fishing as Va*F  
      N_at[t,a] = exp(-M. - Va[a-1]*F)*N_at[(t - 1),(a-1)]
      
      plusGroup = N_at[t,maxAge] + exp(-M - Va[maxAge]*F)*N_at[(t - 1),(maxAge)]
      
      N_at[t,maxAge] = plusGroup
      
    }
    
    Eggs[t] = sum(N_at[t,]*fa*Ma)
    
  }
  
    Out = N_at
  return(Out)
  }
)


```

