Deterministic Age-Stuctured Model with Knife-edge selectivity

##Parameters
 *Linf* - Von Bertalanffy asymptotic length  
 *K* - Von Bertalanffy growth parameter  
 *to* - Von Bertalanffy theoretical length of fish age 0  
 *BHa* - Beverton Holt alpha  
 *BHb* - Beverton Holt beta  
 *Va* - vulnerability to fishing at Age = a  
 *Ma* - Maturity at Age = a  
 *fa* - fecundity at Age = a  (weight of individual * number of eggs produced per gram )
 *M*- natural mortality  
 *F* - fishing mortality  

##Output
 N_at <- dataframe of number of individuals for every age a (cols) at time t (rows)
 
 Catch <- dataframe of number of individuals caought for every age a (cols) at time t (rows)
 
 Revenue <- Splits revenue by 3 commercial size classes 

```{r setup}
rm(list=ls())

library(colorRamps)
library(tidyverse)

#Set Model----
NumYears = 60

R0 = 1000

```


```{r Parameters}
Linf = 122.1
K = 0.172
to = 0.919
  
Wa = 0.024
  
Wb = 2.824
  
maxAge = 18

#Length (cm) at which a fish is 50/95 percent likely to be mature
m50 = 55

m95 = 62.7

#Natural mortality
M <- K * 1.5


#Steepness parameter h - when you dont have a study use 0.7
h=0.7
```



```{r Data}
#Morphology ----

#Our max age is 18 years
Age <- seq(1,maxAge,1)

#Length at median age 
Length <- Linf*(1-exp(-K*((Age + 0.5)-to)))

#Converts lengths (cm) to weight (g)
Weight <- Wa*Length^Wb



#Maturity
Ma = 1/(1 + exp(-log(19)*((Length - m50)/(m95 - m50))))

#realitve fecundity - produce about 41 eggs per gram 
#SOURCE: https://www.scribd.com/doc/81002346/Crecimiento-y-Reproduccion-de-corvina
fa <- Weight*41

#Price per USD per kg is dependent on size of fish
Price <- c(0.71,3.25,4.31)


corvinaperhour = 0.954615805

avgHr.perday = 10

fishingdayspermonth = 20
```


```{r Data Structures}



# Stores abundance in each age cohort

N_at <- data.frame(matrix(data = NA, ncol = max(Age), nrow = NumYears))  
  colnames(N_at) = as.character(c(Age))

# Stores number of total eggs produced in each year   
Eggs <- vector(length = NumYears)

# Sum of abundance_a * weight_a
Biomass <- vector(length = NumYears)

# Stores output of Baranov catch equation summed across cohorts
Catch <- data.frame(matrix(data = NA, ncol = max(Age) + 1, nrow = NumYears)) 
  colnames(Catch) = as.character(c(Age,'Total'))

# Groups biomass by commercial class multiples by price_cc and sums in each year
Revenue <- data.frame(matrix(data = NA, ncol = 4, nrow = NumYears)) 
  colnames(Revenue) = c('small',
                        'med',
                        'large')
                        # ,
                        # 'total')

RevenueTotal = vector(length = NumYears)  

CatchTotal = vector(length = NumYears)  
  
# Stores year
  
year = vector(length = NumYears)

HourFishing = vector(length = NumYears) 

vessels =vector(length = NumYears)
  
```
  
```{r set_scenario}

#Scenario control-----

#Length at first capture
Lc = c(29)

F = seq(0,1, 0.025)

Scenarios = expand.grid(Lc, F) %>%
            mutate(Label = as.vector(outer(Lc, F, paste, sep = "-"))) %>%
            select(Label , F = Var2, Lc = Var1) 


InitialCondition <- c(318.13738, 247.28432, 135.491025, 74.262124, 40.716966, 22.3328194, 12.2540971, 6.7266512, 3.69408854, 2.02963655, 1.11569252, 0.61362030, 0.337674794, 0.185933343, 0.102445509, 5.648386e-02, 3.116534e-02, 3.852763e-02)
```

  
```{r run_model}
  

Model.full = plyr::ddply(Scenarios, 'Label', function(x) {
  
  R0. = R0
  maxAge. = maxAge
  h. = h
  fa. = fa
  Ma. = Ma
  Length. = Length
  Weight. = Weight
  M. = M
  
  F = x$F
  
  Lc = x$Lc
 
  # track model progress
  print(paste("F", F, sep = " = "))
  
  print(paste("Lc", Lc, sep = " = "))

#Pristine Inital condition----    
   
  # #this sets top left
  # N_at[1, 1] = R0.
  # 
  # 
  # #  Set inital condition in year t = 0 (assumes no fishing) 
  # for (a in 2:(maxAge.)) {
  # N_at[1, a] = N_at[1, (a - 1)] * exp(-M.)
  # 
  # }
  # 
  
  
  
  
  
#Overfished Inital condition-----
  N_at[1,] = InitialCondition
  
  Biomass[1] = sum(N_at[1, 1:maxAge.] * Weight.)
  
  #Length (cm) at which a fish is vulnerable to fishing mortality----
  Va = ifelse(Length. < Lc, 0, 1)
  
  #Eggs produced in year 1
  Eggs[1] = sum(N_at[1, ] * fa. * Ma.)
  
  phi <- Eggs[1]
  
  # no catch in year 1
  Catch[1,] = 0
  
  # no revenue in year 1
  Revenue[1,] = 0
  
  
  for (t in 2:NumYears) {
  
  year[t] = t  
    
  #Beverton-Holt spawner recruit relationship-----
  
  N_at[t, 1] = (0.8 * R0. * h. * Eggs[t - 1]) / (0.2 * phi * (1 - h.) + (h. -
  0.2) * Eggs[t - 1])
  
  
  #Abundance in each cohort----
  
  for (a in 2:(maxAge.)) {
  # Introduce fishing as Va*F
    
  N_at[t, a] = exp(-M. - Va[a - 1] * F) * N_at[(t - 1), (a - 1)]
  
  # Additional calculation for group maxAge
  plusGroup = N_at[t, maxAge] + exp(-M - Va[maxAge] * F) * N_at[(t - 1), (maxAge)]
  
  N_at[t, maxAge] = plusGroup
  
  #Catch by cohort = number of individual age a in year t - indvid. age a captured in year t----
  
  Catch[t, a] = (((Va[a] * F) / (Va[a] * F + M)) * N_at[(t), (a)] * (1 - exp(-M - Va[a] * F)))*(Weight[a]/1000)
  
  Catch[t, 1] = 0
  
  }
  
  #store results----
  
  CatchTotal[t] = sum(Catch[t, 1:maxAge])
  
  #Effort calculation 1----
  # 
  #  HourFishing[t] = CatchTotal[t]/corvinaperhour
  # # # 
  #  vessels[t] = HourFishing[t] / (avgHr.perday*fishingdayspermonth*12)
  # # # 
  # 

  
# Calculate Egg production for time t----  
  Eggs[t] = sum(N_at[t, ] * fa * Ma)
  
  #Calculate Revenue by commercial class
  
  Revenue[t, 1] = sum(Catch[t, 1:2] * Price[1] / 1000)
  
  Revenue[t, 2] = sum( Catch[t, 3:4] * Price[2] / 1000)
  
  Revenue[t, 3] = sum(Catch[t, 5:maxAge.] * Price[3] /
  1000)
  
  RevenueTotal[t] = sum(Revenue[t, 1:3])
  
  Biomass[t] <- sum(N_at[t, 1:maxAge.] * Weight.)
  
  }
  
  Out = cbind(year, N_at, CatchTotal, RevenueTotal, Biomass)
  return(Out)
})


```


```{r}
p1 = Model.full %>%
  filter(year == NumYears) %>%
  mutate(mortality = F) %>%
  ggplot(aes(x = vessels, y = (CatchTotal/Biomass))) +
  geom_point() +
  theme_minimal()

plotly::ggplotly(p1)
```

```{r}
p1 = Model.full %>%
  ggplot(aes(x = year, y = RevenueTotal, group = Label, color = Label)) +
  geom_line() +
  theme_minimal()

plotly::ggplotly(p1)
```



```{r}

#devtools::install_github("hafen/trelliscopejs")

Model.full %>%
  #group_by(Label) %>%
  ggplot(aes(x = year, y = RevenueTotal)) +
  geom_point() +
  theme_minimal() +
  trelliscopejs::facet_trelliscope(~Label)


```


   
```{r nesting}
 # prettyPLZ <- PlzWork %>%
 #  as_tibble() %>%
 #  group_by(Label) %>%
 #  nest()
```

