---
title: "Creates Catch Data"
author: "Alex Smith"
date: "April 18, 2016"
output: html_document
---

incopesca_original.xlsx has monthly catch data for every year from 1990-2013 for Guanacaste, Golfo de Nicoya (also "Gulf of Nicoya" ), Quepos, Golfito, Mar Caribe, and Limon. The catch data for each year is on a different sheet. This script joins the mutliple excel sheets into a single data frame and replaces every instance of "Gulf of Nicoya" with "Golfo de Nicoya". 

The output is a .csv file "incopesca_catch" in the 'data' folder. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (basename(getwd())!='data_scripts'){
  setwd('data_scripts')
}
#makes sure you are in the right folder

library(dplyr)
library(readxl) 
library(tidyr)
```

```{r create_dataframe}

catchALL = (lapply(excel_sheets('../data/RAW/incopesca_original.xlsx'),read_excel, path='../data/RAW/incopesca_original.xlsx' )) %>%
            bind_rows() %>%
            filter(!is.na(Region)) %>% #removing entirely blank rows
            as.data.frame()
#creates single data frame from mulitple excel sheets


catchFINAL = catchALL %>%
              mutate(Region=replace(Region, Region=="Gulf of Nicoya", "Golfo de Nicoya")) %>%
              mutate(Species=replace(Species, Species=="CAMARONBLCO.", "CAMARON BLCO.")) %>%
              mutate(Species=replace(Species, Species=="CAMARON BLCO", "CAMARON BLCO.")) %>%
              mutate(Species=replace(Species, Species=="CAMARONCAFE", "CAMARON CAFE")) %>%
              mutate(Species=replace(Species, Species=="CAMARONROSADO", "CAMARON ROSADO"))%>% 
              mutate(Species=replace(Species, Species=="CAMARONCAMELLO", "CAMARON CAMELLO")) %>%
              mutate(Species=replace(Species, Species=="CAMARONROSADO", "CAMARON ROSADO"))%>% 
              mutate(Species=replace(Species, Species=="CAMARONREAL", "CAMARON REAL")) %>%
              mutate(Species=replace(Species, Species=="AGRIACOLA", "AGRIA COLA")) %>%
              mutate(Species=replace(Species, Species=="ALETATIBURON", "ALETA TIBURON"))%>% 
              mutate(Species=replace(Species, Species=="MARLINBLCO.", "MARLIN BLCO.")) %>%
              mutate(Species=replace(Species, Species=="MARLINROS.", "MARLIN ROS.")) %>%
              mutate(Species=replace(Species, Species=="PRIMERA PEG." , "PRIMERA PEQ.")) %>%
              mutate(Species=replace(Species, Species== "PRIMERAPEQ.", "PRIMERA PEQ.")) %>%
              mutate(Species=replace(Species, Species=="PRIMERAGDE.", "PRIMERA GDE.")) 
  
  

#replace every instance of "Gulf of Nicoya" with "Golfo de Nicoya"
#replace every instance of "CAMARONBLCO." with "CAMARON BLCO."

```

```{r write_file}

write.csv(catchFINAL, file = '../data/incopesca_catch.csv')

```

